Crystals

### 2016-12-05 doc/ms.tex
More work on the table
Bit more in the table

>>>>

All of the assumptions are given in Table~\ref{tab:priors}.

\begin{table}
\centering
\begin{tabular}{|lll|}
\hline
{\bf Quantity}      &   {\bf Meaning}   &  {\bf Prior distribution}\\
\hline
{\em Hyperparameters} & &\\
$N$     &   Number of spikes    &  $p(N) \propto 1/(N+1), N \in \{0, 1, ..., 300\}$\\
\hline
{\em Parameters}& &\\
$\sigma_0$ &    Constant noise level  &   $\ln(\sigma_0) \sim \textnormal{Laplace}(0,5)$\\
$\sigma_1$ &    Noise proportionality   &  $\ln(\sigma_1) \sim \textnormal{Laplace}(0,5)$ \\
$\nu$     &   Shape parameter for residuals   &   Loguniform$(1, 1000)$\\
\hline
{\em Data}&&\\
\hline
$\{y_1, y_2, ..., y_n\}$  &   Measurements    & $t(f(x_i; \params), ,\nu)$\\
\hline
{\em Prior information}&&\\
\hline
$n$ & Number of measurements & given\\
$\{x_1, x_2, ..., x_n\}$  & $x$-values of measurements & given \\

\hline
\end{tabular}
\caption{\label{tab:priors}}
\end{table}
